Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-04 Article.tex
Reduce number of self-citations to 3

As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022, Khan-2021}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{Peng-2022} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{Gottstein-2004}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

>>>>

As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{Peng-2022} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{Gottstein-2004}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
